Breakable Elastic-plastic Constraint for\\Rigid Body Simulation

### 2017-07-16 pdocs/thesis/epj-jcgt.tex
jcgt article - eol
minor tuning jcgt article

\author
       {Simo Nikula  Aki Mikkola Timo Björk\\\lut
       }

@@

\begin{abstract}
\small
This paper introduces simple and efficient method to simulate ductile fracture in existing 
impulse-based physics engines.
Method is based on technique of splitting bodies to multiple pieces and joining them with constraints.
Constraints are described using body dimensions and material parameters.

@@

For torque there is a closed form solution only for
circular cross sections.
Given approximation is 
best suited for cases where $b$ and $h$ are similar.
Better approximation for any given $b$ and $h$ can be obtained 
by integrating distance from the center of the joint over cross section and
multiplying it with the yield shear stress e.g. using Octave, \cite{octave}.
An example of calculation of the maximum moment  around $\vec{r}_{anc}^{\,i} $
is shown in Figure \ref{fig:octave-mp}.

>>>>

\author
       {Simo Nikula,  Aki Mikkola, Timo Björk\\\lut
       }

@@

\begin{abstract}
\small
This paper introduces simple and efficient method to simulate ductile fracture in existing 
impulse-based physics engines.
Method is based on technique of splitting bodies to multiple pieces and joining them with constraints.
Procedure to provide realistic parameters for constraints is described.
Procedure is based on body dimensions and material parameters.

@@

For torque there is a closed form solution only for
circular cross sections.
Given approximation is 
best suited for cases where $b$ and $h$ are similar.
Better approximation for any given $b$ and $h$ can be obtained 
by integrating distance from the center of the joint over cross section and
multiplying it with the yield shear stress e.g. using Octave, \cite{octave}.
An example of calculation of the maximum moment  around $\vec{r}_{anc}^{\,i} $
is shown in Listing \ref{lst:octave-mp}.
